Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-03 wearables_survey.tex
finished the related work section!

\subsection{Smartphones and Wearables Concerns}
(REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort. I will talk about how I model Adrienne's work in the next section, Survey, just give a nod to it here and go into it later. Since my results were that people care about privacy, security, health, and social change/social stigma, any phone studies which hint at any of those things will be good to put here. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

Mention any studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod. Especially mention ones on privacy and perceptions, since I know those exist. I doubt there will be ones for social norm shifts/social stigma, or health concerns, but maybe I can at least include some security ones here too. Throughout mentioning all of these works, highlight how my study is different from previous studies.

We are the first study of this kind! Wheee, say it explicitly.

\subsection{Risk Perception}
(REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people. We do this firstly because people are really bad at knowing the likelihood of something, especially a threat with respect to security or privacy, is going to happen (sources here). And while the most damaging situations should also be addressed, this is not yet possible since these technologies haven't been adopted and the damage hasn't happened, so we don't know yet. Additionally, since the number one concern that people had with these devices was privacy (can I say result here? I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.

We also study risk. Mention Fischoff here. This is a very seminal paper in risk perception and it also studies how safe enough something has to be before people can accept something. I will talk about how I model my work in the next section, Survey, just give it a nod here and go into it later. Also mention at least a couple more works related to risk perception here to round it off.

>>>>

\subsection{Smartphones and Wearables Concerns}

There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro} . However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.

\subsection{Risk Perception}

While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology. A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies. In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
